Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.

### 2019-12-13 Ben_Manuscripts/stochastic_transport/Draft.tex
New figures + speed improvements

  We used the 1-mode sFBMcut (see Table~\ref{table:anomalous_models}) anomalous 
  diffusion model in order to demonstrate how one can use its realizations in
  order to calculate the flux (section~\ref{method:mfpt}) of solutes given model 
  parameters extracted from MD simulations. We believe the 1-mode sFBMcut model
  shows the most promising predictive ability of the models studied in this work. 
  %Any approach which allows one to 
  %generate realizations of solute trajectories can be used in place of the AD model.

  %MRS5: One question is if other method would lead to substantially
  %different results for fluxes or selectivity.  May need too think
  %about justification more if just one method is mentioned.

  %MRS5: I think it might be useful to have at least visualizions of
  %distribution of FPT and its fit.  It might not be obvious to
  %readers that the different mechanisms have distributions of FPT
  %that are well decscribed by the relatively simple moving diffusion
  %equation in eq 15.

  %Does't fitting to eq 15 cut down on the expense of the number of trajectories
  %by a fair amount?  Should there be some discussion of this?

  %BJC4: not sure if the next couple paragraphs belong in methods 
  %MRS5: this could potentially be in methods.  Alternatives can be discussed there.
  %BJC5: I tried putting this in methods, but it feels weird without stating the
  % empirical equation. And I'm avoiding stating the empirical model in the methods
  % since it is informed by the data.
  It is computationally infeasible to simulate trajectories long enough that they
  traverse the length of a macroscopic pore. To date, the thinnest H\textsubscript{II}
  LLC membrane synthesized with the monomer in this work was 7$\mu$m thick. Using
  24 cores to simulate trajectory realizations in parallel, it takes on the order 
  of 1 day to simulate 50000 realizations of solutes traversing a 50 nm pore. The 
  RAM requirements and performance scales greater than linearly and thus would 
  take an infeasible amount of memory and time to simulate transport through a 
  pore over 100 times longer.

  We used simulated trajectories which traverse computationally-reasonable length
  pores in order to construct an empirical model which one can use to estimate 
  particle flux for arbitrary length pores. As shown in Figure~\ref{fig:flux_curves},
  the flux appears to scale according to a power law of the form:
  \begin{equation}
  J(L) = cL^{-\beta} 
  \label{eqn:flux_decay}
  \end{equation}
  %while the MFPT scales as its inverse, $(1/c)L^{\beta}$.

@@

  %BJC: need simulations with increased length for L=35-50 nm pores of acetic acid and methanol
  %BJC: see of clauset has better way of fitting t^-alpha (alpha might be too big)
  %BJC: not sure mfpt is necessary. Takes up space.
  %BJC: change alpha to beta
  %BJC: make a chart with parameters
  %BJC: should have a paragraph about c -- roughly follows their MSDs.
  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{flux_curves.pdf}
  \caption{Fits to $cL^{-\beta}$}\label{fig:flux_curves_regular}
  \end{subfigure}
  % BJC: could use better color scheme. Maybe outline hurst parameters
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{c_parameters.pdf}
  \caption{}\label{fig:c_parameters}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{beta_parameters.pdf}
  \caption{}\label{fig:beta_parameters}
  \end{subfigure}
%  \begin{subfigure}{0.475\textwidth}
%  \includegraphics[width=\textwidth]{mfpt_curves.pdf}
%  \caption{}\label{fig:mfpt_curves}
%  \end{subfigure}
  %BJC: going out to 3 decimal places seems silly
  %BJC: might get closer to beta=2 if I use different curve fitting technique than fitting line to log-log
%  \begin{subfigure}{0.325\textwidth}
%  \includegraphics[width=\textwidth]{flux_curves_brownian.pdf}
%  \caption{Fixed $H=0.5$}\label{fig:flux_curves_brownian}
%  \end{subfigure}
%  \begin{subfigure}{0.475\textwidth}
%  \includegraphics[width=\textwidth]{mfpt_curves_brownian.pdf}
%  \caption{}\label{fig:mfpt_curves_brownian}
%  \end{subfigure}
  %MRS5: the b) pane is a little messy.  If c) is moved to the supporting, maybe can make b into two figures, and 
  % have each just show 1 point? 
  \caption{(a) The single particle solute flux decays with increasing pore length. 
  Solutes with high MSDs have higher fluxes. (b) We fit the single particle solute flux 
  versus pore length, $L$, to a power law function of the form $cL^{-\beta}$ (dashed 
  lines in (a)). Solutes with higher fluxes have higher values of $c$. Solutes with 
  smaller Hurst parameters, $H$, have larger values of $\beta$. (c) If we remove 
  correlation between hops (set $H$=0.5), the flux increases significantly and 
  $\beta \sim 2$ for all solutes independent of dwell distribution
  parameters.}\label{fig:flux_curves}
  \end{figure}

>>>>

  We used the 1-mode sFBMcut (see Table~\ref{table:anomalous_models}) anomalous 
  diffusion model in order to demonstrate how one can use its realizations in
  order to calculate the flux (section~\ref{method:mfpt}) of solutes given model 
  parameters extracted from MD simulations. The sFLMcut model and MSDDM yield 
  similar predictions at a much greater computational cost due to the slow
  generation of fractional L\'evy noise.
  %MRS5: One question is if other method would lead to substantially
  %different results for fluxes or selectivity.  May need too think
  %about justification more if just one method is mentioned.
  %BJC5: would love to test MSDDM against this but I don't know how to make 
  % the algorithm faster. It already uses an FFT to correlate the data (to which I pass powers of 2)

  %MRS5: I think it might be useful to have at least visualizions of
  %distribution of FPT and its fit.  It might not be obvious to
  %readers that the different mechanisms have distributions of FPT
  %that are well decscribed by the relatively simple moving diffusion
  %equation in eq 15. 
  %BJC5: added to figure

  %BJC4: not sure if the next couple paragraphs belong in methods 
  %MRS5: this could potentially be in methods.  Alternatives can be discussed there.
  %BJC5: I tried putting this in methods, but it feels weird without stating the
  % empirical equation. And I'm avoiding stating the empirical model in the methods
  % since it is informed by the data.
  It is computationally infeasible to simulate trajectories long enough that they
  traverse the length of a macroscopic pore. To date, the thinnest H\textsubscript{II}
  LLC membrane synthesized with the monomer in this work was 7$\mu$m thick. Using
  24 cores to simulate trajectory realizations in parallel, it takes on the order 
  of 1 day to simulate 10000 realizations of solutes traversing a 50 nm pore. The 
  RAM requirements and performance scales greater than linearly and thus would 
  take an infeasible amount of memory and time to simulate transport through a 
  pore over 100 times longer.

  We used simulated trajectories which traverse computationally-reasonable length
  pores in order to construct an empirical model which one can use to estimate 
  particle flux for arbitrary length pores. We fit Equation~\ref{eqn:passage_times}
  to the empirical distribution of first passage times in Figure~\ref{fig:fpt_distributions}
  and used the expected value of the analytical equation to calculate flux from 
  Equation~\ref{eqn:hill_relation}. As shown in Figure~\ref{fig:flux_curves}, 
  the flux appears to scale according to a power law of the form:
  \begin{equation}
  J(L) = cL^{-\beta} 
  \label{eqn:flux_decay}
  \end{equation}
  %while the MFPT scales as its inverse, $(1/c)L^{\beta}$.

  %BJC: need simulations with increased length for L=35-50 nm pores of acetic acid and methanol
  %BJC: see of clauset has better way of fitting t^-alpha (alpha might be too big)
  %BJC: should have a paragraph about c -- roughly follows their MSDs.
  \begin{figure}
  \centering
  \begin{subfigure}{0.475\textwidth}
  \includegraphics[width=\textwidth]{fpt_distributions.pdf}
  \caption{}\label{fig:fpt_distributions}
  \end{subfigure}
  \begin{subfigure}{0.475\textwidth}
  \includegraphics[width=\textwidth]{flux_curves.pdf}
  \caption{}\label{fig:flux_curves_regular}
  \end{subfigure}
  % BJC: could use better color scheme. Maybe outline hurst parameters
  \begin{subfigure}{0.475\textwidth}
  \includegraphics[width=\textwidth]{c_parameters.pdf}
  \caption{}\label{fig:c_parameters}
  \end{subfigure}
  \begin{subfigure}{0.475\textwidth}
  \includegraphics[width=\textwidth]{beta_parameters.pdf}
  \caption{}\label{fig:beta_parameters}
  \end{subfigure}
%  \begin{subfigure}{0.475\textwidth}
%  \includegraphics[width=\textwidth]{mfpt_curves.pdf}
%  \caption{}\label{fig:mfpt_curves}
%  \end{subfigure}
  %BJC: going out to 3 decimal places seems silly
  %BJC: might get closer to beta=2 if I use different curve fitting technique than fitting line to log-log
%  \begin{subfigure}{0.325\textwidth}
%  \includegraphics[width=\textwidth]{flux_curves_brownian.pdf}
%  \caption{Fixed $H=0.5$}\label{fig:flux_curves_brownian}
%  \end{subfigure}
%  \begin{subfigure}{0.475\textwidth}
%  \includegraphics[width=\textwidth]{mfpt_curves_brownian.pdf}
%  \caption{}\label{fig:mfpt_curves_brownian}
%  \end{subfigure}
  %MRS5: the b) pane is a little messy.  If c) is moved to the supporting, maybe can make b into two figures, and 
  % have each just show 1 point? 
  \caption{(a) The single particle solute flux decays with increasing pore length. 
  Solutes with high MSDs have higher fluxes. (b) We fit the single particle solute flux 
  versus pore length, $L$, to a power law function of the form $cL^{-\beta}$ (dashed 
  lines in (a)). Solutes with higher fluxes have higher values of $c$. Solutes with 
  smaller Hurst parameters, $H$, have larger values of $\beta$. (c) If we remove 
  correlation between hops (set $H$=0.5), the flux increases significantly and 
  $\beta \sim 2$ for all solutes independent of dwell distribution
  parameters.}\label{fig:flux_curves}
  \end{figure}

  %MRS5: Does't fitting to eq 15 cut down on the expense of the number of trajectories
  %by a fair amount?  Should there be some discussion of this? 
  %BJC5: added this
  Although we used 10000 trajectory realizations in order to generate 
  Figure~\ref{fig:flux_curves}, one may actually need considerably less realizations
  in order to predict and compare flux between solutes. In Figure~\ref{S-fig:flux_curve_sensitivity}
  of the Supporting information, we show that one can still show statistically
  significant differences in solute flux with as little as 100 trajectory 
  realizations.

@@
